\documentclass[12pt]{article}

\usepackage[margin=1.2in]{geometry}
%\usepackage{supertabular}
%\usepackage{setspace}
%\doublespacing
%\usepackage{graphicx}
\usepackage{hyperref}


\newcommand{\company}[1]{\verb|#1|}
\newcommand{\software}[1]{\verb|#1|}
\newcommand{\term}[1]{{\ttfamily #1}}
\newcommand{\project}[1]{\texttt{#1}}
\newcommand{\comment}[1]{ [ \textit{#1} ] }


\author{Ivan Savov}
\title{ {\Huge Idea collector } }

\begin{document}
\maketitle

\abstract{	
    A scripted series of questions that can help someone hooked up on ``brain crack''\cite{ze} clarify his thoughts. The script collects general info like title, authors and tags and then asks a number of questions depending on the ``type'' of idea. Can be distributed as a standalone python script or some web interface.
}

{\bf keywords: } entrepreneurship, python, startup, 


\section{Previous technology}

	There are many sites for project management I am sure.
	
    
\section{New technology}

	Script that forces you to think about all the different aspects of your idea, not just
	the ones you tend to think about.
	
	There is a possibility you can make the script very intelligent connecting many sources
	of information so that you can manage your ideas more easily.	
	
	\begin{itemize}
		\item 	Create a ``folder'' for your idea (verison control?)
		\item	Create beautiful latex doc from your proj
		\item	Create a simple dokuwiki for your project
		\item 	If you allow it to touch your bookmarks folder, the script can automatically ``guess'' which
				of the links you saved are relevant and include them in the references section.
		\item	When it asks you for {\bf what is next?} it can set reminders for you and bug you if 
				you aren't working on your idea.
	\end{itemize}
	
	
	Ideally there will be pluggable modules of \term{questions}, \term{actions} and 
	\term{workflows} that can be user contributed and shared.
	
	
\section{Why is it better?}

	The main advantage is that the series of questions act as a template for your thinking. 
	I \emph{really} need this kind of template right now to organize my projects so I assume
	that other people will be interested in such a product.
	
    
\section{Next steps}
 
 
 
 \begin{thebibliography}{bcrack}
%
%
\bibitem[ze]{ze}   ze frank show \textit{Where do ideas come from?}\\
                           \url{http://www.zefrank.com/theshow/archives/2006/07/071106.html}
%
\end{thebibliography}

\end{document}
